### 2023-11-12 sections/4-results.tex
headers for new datasets and naming fixes

Figure \ref{fig:results:random-scaling} displays results for a random datset with the same dimensionality and cardinality as Sift (i.e., 128 and 1,000,000 respectively). 
These results illustrate the fact that \emph{ceteris paribus}, absent a manifold structure in the dataset, CAKES's algorithms do not begin to outperform linear search until the cardinality multiplier is around 10. 
Repeated $\rho$-NN shows significantly worse performance on this dataset relative to both the other algorithms and to its own performance on real datasets. 
This is unsurprising, given that RepeatedRnn relies on a low local fractal dimension around the query in order to quickly home in on the correct radius for $k$ hits. 
With a completely random dataset, whose average local fractal dimension will be near its embedding dimension, RepeatedRnn will meander for longer before finding this correct radius.

>>>>

Figure \ref{fig:results:random-scaling} displays results for a random datset with the same dimensionality and cardinality as Sift (i.e., 128 and 1,000,000 respectively). 
These results illustrate the fact that \emph{ceteris paribus}, absent a manifold structure in the dataset, CAKES's algorithms do not begin to outperform linear search until the cardinality multiplier is around 10. 
Repeated $\rho$-NN shows significantly worse performance on this dataset relative to both the other algorithms and to its own performance on real datasets. 
This is unsurprising, given that Repeated $\rho$-NN relies on a low local fractal dimension around the query in order to quickly home in on the correct radius for $k$ hits. 
With a completely random dataset, whose average local fractal dimension will be near its embedding dimension, Repeated $\rho$-NN will iterate for longer before finding this correct radius.
